Emittance preservation of an electron bunch in a loaded quasi-linear plasma wakefield

### 2017-07-06 Tex/Paper.tex
Added text and made some layout updates

\documentclass[aps,prstab,reprint,amsmath,amssymb,groupedaddress]{revtex4-1}
\bibliographystyle{apsrev}

@@

In order to evaluate the quality of the beam, we also needed to study its emittance. Full PIC codes like Osiris are
voulnerable to numerical growth of emittance caused by the ``numerical Cherenkov effect'' \cite{godfrey:1974}. This is a
know issue with the Yee EMF solver, which causes the phase velocity of electromagnetic fields to be lowet than $c$,
while the beam moves very close to $c$. The effect can be mitigated somewhat by a the Lehe solver \cite{lehe:2013}, but
the effect is still prominent in the the high density regions of the electron beam.

@@

\subsection[\label{S:M:Setup}]{Simulationn Setup}

@@

%~ - the electron beam blows out the remaining plasma electrons. The transverse fields are dominated by the linear
%~   focusing fields originating from the ion background, leading to emittance preservation of the part of the electron
%~   beam inside the bubble [loading of a quasi-linear wake, and still get emittance preservation: this is new]
%~   (simulation results to show: loaded wake, with bubble - many different aspects of this, trans., long. field,
%~   electron densities etc. )
%~ - the acceleration and the transverse emittance stable on long timescales (simulation results to show: transverse and
%~   longitudinal phase spaces, space long simulation)
%~ - in this regime, emittance preservation is robustness to drive-witness offset [this is new] (simulation results to
%~   show: transverse and longitudinal phase spaces, long offset simulation)

>>>>

\documentclass[aps,prstab,reprint,amsmath,amssymb,groupedaddress]{revtex4-1}
\bibliographystyle{apsrev4-1}
\usepackage{hyperref}
\hypersetup{colorlinks=true, citecolor=blue, urlcolor=blue, linkcolor=blue}

@@

In order to evaluate the quality of the beam, we also needed to study its emittance. Full PIC codes like Osiris are
vulnerable to numerical growth of emittance caused by the ``numerical Cherenkov effect'' \cite{godfrey:1974}. This is a
know issue with the Yee EMF solver, which causes the phase velocity of electromagnetic fields to be lowet than $c$,
while the beam moves very close to $c$. The effect can be mitigated somewhat by a the Lehe solver \cite{lehe:2013}, but
the effect is still prominent in the the high density regions of the electron beam.

@@

\subsection[\label{S:M:Setup}]{Simulation Setup}

In these simulations we use a single proton drive bunch that sets up a wakefield comparable to that which we expect to
see from the self-modulated SPS beam. This was done both to reduce simulation time, as we run 3D simulations, and to
create a stable environment for the witness beam.

@@

%~ - the electron beam blows out the remaining plasma electrons. The transverse fields are dominated by the linear
%~   focusing fields originating from the ion background, leading to emittance preservation of the part of the electron
%~   beam inside the bubble [loading of a quasi-linear wake, and still get emittance preservation: this is new]
%~   (simulation results to show: loaded wake, with bubble - many different aspects of this, trans., long. field,
%~   electron densities etc. )

%~ - the acceleration and the transverse emittance stable on long timescales (simulation results to show: transverse and
%~   longitudinal phase spaces, space long simulation)

%~ - in this regime, emittance preservation is robustness to drive-witness offset [this is new] (simulation results to
%~   show: transverse and longitudinal phase spaces, long offset simulation)
